INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-20 paper/paper.tex

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

@@

>>>>

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{siunitx}

@@

\subsection{Optimization problem}

\begin{table}
    \caption{Result of the optimization with FOM and ROM.}\label{tab:minimization_data}
    \centering
    \input{./src/beam/tables/minimization_data.tex}
\end{table}

\begin{table}
    \caption{Comparison of reduced optimal solution $\mu_N^{\ast}$ and true optimal solution $\mu^{\ast}$.}\label{tab:minimization_comparison}
    \centering
    \input{./src/beam/tables/minimization_comparison.tex}
\end{table}
